Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-25 Scripts/Initial_Analysis.Rmd
changes for testing

data_type <- "Catch"
ensamble_list <- seq(102,103,1)
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()

@@

spp_list <- unique(Transboundary_spp$taxon_key)[1:3]

@@

```{r Proportion_routine, eval = T, echo = F}
####_______________________ ####
# Estimating proportion change
####_______________________ ####

@@

mclapply(
  spp_list, #c(600004,600005),
  EstPropChange,
  year <- year_df,
  data_type <- "Catch",
  ensamble_list = ensamble_list,
  path = DBEM_path,
  neighbours = Neighbours
)

>>>>

data_type <- "Catch"
ensamble_list <- seq(102,111,1)
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()

@@

spp_list <- unique(Transboundary_spp$taxon_key)

@@

```{r Proportion_routine, eval = T, echo = F}

####_______________________ ####
# Estimating proportion change
####_______________________ ####

@@

mclapply(
  spp_list[1],
  EstPropChange,
  year <- year_df,
  data_type <- "Catch",
  ensamble_list = ensamble_list[1],
  path = DBEM_path,
  neighbours = Neighbours
)
